---
title: "Results"
author: "IPM"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Feature selection
We used two feature selection method, *mRMR* and *LASSO* to select the feature. At first, *mRMR* was performed to eliminate the redundant and irrelevant features, 30 features were retained. Then *LASSO* was conducted to choose the optimized subset of features to construct the final model.

#### LASSO

1. The LASSO includes choosing the regular parameter $\lambda$, determining the number of the feature.

```{r, echo = FALSE, fig.height=9}
oldpar <- par(mfrow = c(2, 1))
plot(cvfit)
# figure2
plot(fit, s = s, xvar = 'lambda')
abline(v = log(cvfit$lambda.min), lty = 2)
par(oldpar)
```

2. After the number of feature determined, the most predictive subset of feature was chosen and the corresponding coefficients were evaluated.

```{r, echo = FALSE}
p_coef + theme(axis.text.y = element_text(size = 12))

```

### Radiomics signature construction
#### Radscore

Radscore was calculated by summing the selected features weighted by their coefficients. The final formula of radscore is:
```{r, echo = FALSE}
print(radscore)
```

And we compared the radscores from class 0 and class 1 on training group and test group respectively.
```{r, warning=FALSE}
ggarrange(p_train, p_test, ncol = 2)
```

#### Radiomics valiation
We used ROC analysis to evaluate the performance of the model：  

```{r, fig.width=10}
oldpar <- par(mfrow = c(1, 2))
plot(roc_res_train, print.auc = T, 
     print.auc.pattern = 'AUC: %.2f(%.2f-%.2f)', legacy.axes = T)

# figure4
plot(roc_res_test, print.auc = T, legacy.axes = T,
     print.auc.pattern = 'AUC: %.2f(%.2f-%.2f)')

par(oldpar)
```

Based on Youden Index, other parameters were calculated as following:

```{r}
knitr::kable(rec_all, caption = 'Result of radiomics')
```

### Nomogram build

#### Clinicopathological factors and radscore selection

```{r, echo = FALSE}
glmSeries(Label~1, data = dt_cli_train_1, vars = colnames(dt_cli_train_1)[-1], 
          family = 'binomial')
```

```{r, echo = F}
{
  publish(log_fit_final)
}
```

#### nomogram
```{r, echo = F}
plot(nom_com)
```

#### nomogram validation

```{r, echo = F, fig.width=10}
oldpar <- par(mfrow = c(1, 2))
cal_train <- calPlot2(mod_train, data = dt_combined_train_final, 
                      legend = F, col = 	'#FF6EB4', lty = 2)
cal_test <- calPlot2(mod_train, data = dt_combined_test_final,
                     legend = F, col = 	'#FF6EB4', lty = 2)
par(oldpar)
```

Hosmer-Lemeshow Test results:
```{r, echo = F}
HosmerLemeshowTest(cal_train$Frame$lrm, cal_train$Frame$jack)
HosmerLemeshowTest(cal_test$Frame$lrm, cal_test$Frame$jack)
```

Finally, we used decision curve to evaluate the clinical usefullness of the model:

```{r}
plot_decision_curve(list(dca1, dca2), confidence.intervals = F, 
                    col = c('red', 'green', 'blue', 'black'), 
                    curve.names = c('With Radscore', 'Without Radscore'),
                    legend.position = 'topright', cost.benefits = FALSE)
```

